---
title: "Secondary Tasks Analysis"
output:
  rmdformats::html_clean:
    highlight: espresso
    lib_dir: ".libs/"
    toc: true
author:
  - "John Kafumbe"
  - "Jeffrey Olsen"
date: "`r format(Sys.time(), '%B %d, %Y')`"
---

```{r setup}
#| include = FALSE

knitr::opts_chunk$set(
  echo = TRUE,
  cache = TRUE,
  autodep = TRUE,
  fig.path = ".figures/",
  cache.path = ".cache/",
  fig.width = 7,
  fig.height = 5,
  dev = "svglite"
)

library(tidyverse)
library(dplyr)
library(lme4)
library(lmerTest)
library(glue)
library(mgcv)
library(data.table)
library(this.path)
library(glmmTMB)
library(sjPlot)
library(performance)
library(visreg)
library(modelsummary)
library(emmeans)
library(plotly)
library(qs2)
library(downloadthis)

dir.create("./output", showWarnings = FALSE)
```

<div style="text-align: center;">
```{r Download Rmd}
#| echo = FALSE

download_file(
  this.path(),
  button_label = "Download Rmd",
  button_type = "primary",
  has_icon = TRUE,
  self_contained = TRUE
)
```
</div>

```{r Read in data}
#| cache = FALSE,
#| include = FALSE

setwd(this.dir())

if (!file.exists("./data/processed_data.qs") |
  file.mtime("./data/processed_data.qs") <
    file.mtime("./data_processing.R")) {
  processing_env <- new.env()
  source("./data_processing.R", local = processing_env)
  list2env(as.list(processing_env), envir = globalenv())
} else {
  qs_readm("./data/processed_data.qs")
}
```

```{r Helpers}
#| include = FALSE

generate_table <- function(
  model,
  title,
  shape = term ~ statistic,
  align = "lrcrc",
  ...
) {
  modelsummary(
    list(" " = model),
    ...,
    title = title,
    output = "latex",
    stars = TRUE,
    shape = shape,
    estimate = c("Estimate" = "{estimate}"),
    statistic = c(
      "95\\symbol{37} CI" = "({conf.low}, {conf.high})",
      "p-value" = "{p.value}",
      " " = "{stars}"
    ),
    align = align,
    coef_rename = c(
      "(Intercept)" = "Intercept",
      "BAC" = "BrAC",
      "KSS_cent" = "KSS (median-centered)",
      "PhaseTask" = "Phase (Task)",
      "Road_SurfacePaved" = "Road surface (Paved)",
      "as.numeric(Drive)" = "Drive \\#",
      "SD (Intercept Subject)" = "Subject intercept SD",
      "Lat_Dev_abs_init" = "Initial lateral deviation"
    ),
    gof_map = data.frame(
      raw = c("nobs", "r2.marginal", "r2.conditional"),
      clean = c("N", "Marginal $R^2$", "Conditional $R^2$"),
      fmt = c(0, 3, 3)
    ),
    escape = FALSE,
    notes = list("+ p < 0.1, * p < 0.05, ** p < 0.01, *** p < 0.001")
  ) %>%
    as.character() %>%
    str_replace_all(
      c(
        "component" = "Component",
        "conditional" = "Conditional",
        "zero_inflated" = "Zero-inflated",
        "dispersion" = "Dispersion"
      )
    ) %>%
    write_lines(glue("./output/{str_replace_all(title, ' ', '_')}.tex"))
}
```

## Preliminary models

```{r Preliminary models}
# Fit mixed-effects model to predict deviation differences
# across drives, with random intercepts for subjects

model2 <- lmer(Deviation_Frames_prop_diff ~ factor(Drive) + (1 | Subject),
  data = wideform_task_matrix
)
summary(model2)

# Model testing the fixed effects of alcohol (BAC) and fatigue (KSS) on
# averaged bilateral pupil reactivity,
# controlling for individual baseline variance

model3 <- lmer(Avg_Pupil_Diameter_mean_diff ~ BAC + KSS_cent + (1 | Subject),
  data = wideform_task_matrix
)
summary(model3)

# SDLP Model predicted by alcohol and fatigue

model_sdlp <- lmer(Lat_Dev_SD_diff ~ BAC + KSS_cent + (1 | Subject),
  data = wideform_task_matrix
)
summary(model_sdlp)

# Speed_SD_Diff model predicted by alcohol and fatigue

model_speed <- lmer(Speed_SD_diff ~ BAC + KSS_cent + (1 | Subject),
  data = wideform_task_matrix
)
summary(model_speed)

# Lane departure proportion difference (you already build this column)
model_dev <- lmer(Deviation_Frames_prop_diff ~ BAC + KSS_cent + (1 | Subject),
  data = wideform_task_matrix
)
summary(model_dev)

print(t.test(wideform_task_matrix$Avg_Pupil_Diameter_mean_diff))
print(t.test(wideform_task_matrix$Lat_Dev_SD_diff))
print(t.test(wideform_task_matrix$Speed_SD_diff))
print(t.test(wideform_task_matrix$Per_Close_diff))
print(t.test(wideform_task_matrix$Brake_Force_mean_diff))
```

## Preliminary lane deviation analysis

```{r Preliminary lane deviation analysis}
#| fig.height = 10,
#| out.width = "100%"

ggplot(
  data = task_matrix,
  aes(x = Deviation_Frames_prop)
) +
  geom_density() +
  geom_vline(
    aes(xintercept = mean(filter(
      task_matrix,
      Drive == 1 & Phase == "Control"
    )$Deviation_Frames_prop)),
    linetype = "dashed"
  ) +
  facet_wrap(~ Drive + Phase, ncol = 2) +
  xlim(0, 1)
```

## Distributions of deviation proportion differences by drive

```{r Distributions of deviation proportion differences by drive}
# Limit to tasks where there was at least one frame of deviation before or after
ggplot(
  data = wideform_task_matrix %>% filter(
    Deviation_Frames_prop_Task != 0 |
      Deviation_Frames_prop_Control != 0
  ),
  aes(x = Deviation_Frames_prop_diff)
) +
  geom_density() +
  facet_wrap(~Drive) +
  xlim(-1, 1)
```

## Plots of trends across individuals

```{r Plots of trends across individuals}
#| fig.show = "hold"

# Average pupil diameter
ggplot(
  data = non_aug %>%
    group_by(Subject, Drive, Frame_Num) %>%
    mutate(Avg_Pupil_Diameter_mean = mean(
      Avg_Pupil_Diameter,
      na.rm = TRUE
    )) %>%
    ungroup(),
  aes(x = Frame_Num, y = Avg_Pupil_Diameter_mean, color = Subject)
) +
  geom_smooth(
    linewidth = 0.1,
    se = FALSE,
    method = "bam",
    formula = y ~ s(x, bs = "cs")
  ) +
  facet_wrap(~Drive) +
  theme(legend.position = "NONE")
```

## Box plots to compare control & task phases

```{r Box Plots for task matrix}
plot_data <- task_matrix %>% filter(!is.na(Avg_Pupil_Diameter_mean))

ggplot(plot_data, aes(x = Phase, y = Avg_Pupil_Diameter_mean)) +
  geom_boxplot(alpha = 0.7, outlier.alpha = 0.3) +
  theme_minimal() +
  labs(title = "Pupil Dilation: Anticipation vs Reaction")
```

## Plots of trends around button presses

```{r Plots of trends around button presses}
# Get left button press indices
left_button_press_indices <- filter(non_aug, Left_Button_Press == 1)$X

# Create a list of filtered data frames
obs_around_press <- bind_rows(lapply(
  unique(task_matrix$Frame_Index),
  function(press) {
    frames_in_segment <- filter(
      task_matrix,
      Frame_Index == press
    )[[1, "Reaction_Frames"]]

    non_aug[seq(
      press - frames_in_segment,
      press + frames_in_segment - 1
    ), ] %>%
      mutate(
        Press_Frame = press,
        Frame_in_Segment = X - press + frames_in_segment + 1,
        Adj_Frame_in_Segment = -100 +
          (((Frame_in_Segment - min(Frame_in_Segment)) * 200) /
            (max(Frame_in_Segment) - min(Frame_in_Segment)))
      )
  }
))

plot_metric_around_task <- function(variable, ymin, ymax, subject) {
  ggplot(
    data = filter(
      obs_around_press,
      Subject == subject,
    ),
    aes(
      x = Adj_Frame_in_Segment,
      y = .data[[variable]],
      color = factor(Press_Frame),
    )
  ) +
    geom_line(linewidth = 0.1) +
    theme(legend.position = "NONE") +
    geom_vline(xintercept = 0, linewidth = 1) +
    labs(
      title = glue("All button presses: Subject {subject}"),
      x = "Time (relative to press)",
      y = variable
    ) +
    ylim(ymin, ymax) +
    facet_wrap(~Drive, ncol = 2, scales = "free")
}

metrics <- list(
  list(variable = "Avg_Pupil_Diameter", ymin = 0, ymax = 6),
  list(variable = "Vehicle_Lat_Dev", ymin = -6, ymax = 6)
)
for (metric in metrics) {
  print(plot_metric_around_task(metric$variable, metric$ymin, metric$ymax, 1))
}
```

Interpretability relies on the assumption that trends in eye metrics
change faster/slower proportional to the task reaction time.

## Pupil diameter by KSS and drive

```{r Pupil diameter by KSS and drive}
eye_kss <- non_aug %>%
  filter(!is.na(Avg_Pupil_Diameter) & !is.na(KSS_Score)) %>%
  select(KSS_Score, Frame_Num, Drive, Avg_Pupil_Diameter) %>%
  group_by(KSS_Score, Frame_Num, Drive) %>%
  summarize(
    Avg_Pupil_Diameter = mean(Avg_Pupil_Diameter),
    .groups = "drop"
  )

ggplot(
  data = eye_kss,
  aes(
    x = Frame_Num,
    y = Avg_Pupil_Diameter,
    group = factor(KSS_Score),
    color = as.numeric(as.character(KSS_Score))
  )
) +
  geom_smooth(
    linewidth = 0.3, se = FALSE,
    method = "bam", formula = y ~ s(x, bs = "cs")
  ) +
  facet_wrap(~Drive) +
  theme(legend.position = "bottom") +
  scale_color_viridis_c(name = "KSS", direction = -1) +
  ylim(0, 6)

pupil_diameter_diff_model <- lmer(
  Avg_Pupil_Diameter_mean_diff ~
    BAC +
    KSS_cent +
    as.numeric(Drive) +
    (1 | Subject),
  data = wideform_task_matrix
)
summary(pupil_diameter_diff_model)
check_collinearity(pupil_diameter_diff_model)
```

## Reaction time by subject, drive, KSS

```{r "Reaction time by subject, drive, KSS"}
#| out.width = "100%"

# Line plot
task_matrix %>%
  drop_na(KSS, Subject, Drive, Reaction_Frames) %>%
  group_by(Subject, Drive, KSS) %>%
  summarize(
    Reaction_Time = mean(Reaction_Frames) * (1000 / 60),
    .groups = "drop"
  ) %>%
  {
    ggplot(
      data = filter(
        .,
        as.numeric(Subject) %in% sample(
          unique(task_matrix$Subject),
          10
        )
      ),
      aes(x = Drive, y = Reaction_Time, group = Subject)
    ) +
      geom_point(aes(color = KSS), size = 3) +
      geom_line() +
      labs(x = "Drive", y = "Reaction time (ms)", color = "KSS score") +
      scale_color_continuous(breaks = 1:9, limits = c(1, 9))
  }

# Heat map
task_matrix %>%
  drop_na(KSS) %>%
  group_by(Drive, KSS) %>%
  summarize(
    Reaction_Time = median(Reaction_Frames) * (1000 / 60),
    Total_tasks = n(),
    .groups = "drop"
  ) %>%
  complete(KSS, Drive) %>%
  {
    ggplot(
      data = .,
      aes(y = factor(KSS), x = Drive)
    ) +
      geom_tile(aes(fill = Reaction_Time)) +
      scale_fill_gradient(
        low = "royalblue",
        high = "springgreen",
        na.value = "gray"
      ) +
      coord_cartesian(expand = FALSE) +
      theme_minimal() +
      labs(x = "Drive", y = "KSS score", fill = "Reaction time (ms)")
  }

# Box plot
wideform_task_matrix %>%
  mutate(Reaction_Time = Reaction_Frames * (1000 / 60)) %>%
  drop_na(Phase_Control, KSS) %>%
  {
    ggplot(
      data = .,
      aes(x = factor(KSS), y = Reaction_Time)
    ) +
      geom_boxplot(outlier.shape = NA) +
      facet_wrap(~Drive) +
      ylim(0, 4000) +
      labs(x = "KSS score", y = "Reaction time (ms)")
  }
```

Currently samples 10 drivers. In the future we could group them by
some trait and aggregate across drivers within groups.

## Saccades ZIP model

```{r Saccades ZIP model}
#| out.width = "100%"

ggplot(task_matrix, aes(x = Saccade_Count)) +
  geom_histogram(binwidth = 0.5) +
  facet_wrap(~Phase)

model_saccade_zip <- glmmTMB(
  Saccade_Count ~ Phase + BAC + KSS_cent + Road_Surface + (1 | Subject),
  ziformula = ~1, # What predicts being in the "zero" group?
  family = poisson,
  data = task_matrix
)
summary(model_saccade_zip)
```

## Saccade binary visualizations

```{r Saccade binary visualizations}
task_matrix %>%
  mutate(Zero_Saccade = Saccade_Count == 0) %>%
  group_by(Drive, Phase) %>%
  summarize(
    Prop_Zero = mean(Zero_Saccade),
    SE = sd(Zero_Saccade) / sqrt(n()),
    .groups = "drop"
  ) %>%
  ggplot(aes(
    x = factor(Drive),
    y = Prop_Zero,
    fill = factor(Phase,
      labels = c(
        "Control",
        "Task"
      )
    )
  )) +
  geom_col(position = "dodge") +
  labs(
    x = "Drive",
    y = "Proportion of segments with zero saccades",
    fill = "Phase"
  ) +
  theme_minimal()
```

## Saccade logit

```{r Saccade logit}
saccade_logit_model <- glmer(
  data = task_matrix,
  formula =
    (Saccade_Count > 0) ~
      BAC +
      KSS_cent +
      Road_Surface +
      BAC * KSS_cent +
      # BAC * Phase +
      as.numeric(Drive) +
      Phase +
      (1 | Subject),
  family = "binomial"
)
summary(saccade_logit_model)
```

Including an interaction term between BAC and Phase, there was no evidence
($p = 0.11$) that the the effect of BAC on saccades is less (in magnitude) in
the task segment than in the control group.
There was no evidence to suggest a difference in BAC effect on saccades
between the control and pre-task segments.

A similar model with an interaction term between phase and drive number
was not better-fitting when accounting for the additional parameters.

## Reaction time by SDLP prior to task

```{r Reaction time by SDLP prior to task}
#| out.width = "100%"

model_rt_driving <- lmer(
  (Reaction_Frames * (1000 / 60)) ~
    BAC +
    KSS_cent +
    Road_Surface +
    as.numeric(Drive) + # Drive term to adjust for learning effect
    (1 | Subject),
  data = wideform_task_matrix
)
summary(model_rt_driving)

wideform_task_matrix %>%
  drop_na(Lat_Dev_SD_Control, Reaction_Frames, Drive, KSS) %>%
  mutate(Drive = factor(
    Drive,
    labels = c(
      "Drive 1",
      "Drive 2",
      "Drive 3",
      "Drive 4",
      "Drive 5"
    )
  )) %>%
  ggplot(aes(
    x = Lat_Dev_SD_Control,
    y = Reaction_Frames * (1000 / 60),
    color = KSS
  )) +
  geom_point(alpha = 0.3, size = 1.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black", linewidth = 0.5) +
  scale_color_viridis_c(direction = -1) +
  facet_wrap(~Drive) +
  labs(
    x = "Lateral deviation SD before press (ft)",
    y = "Reaction time (ms)",
    color = "KSS",
    title = "Control frame driving stability vs reaction time",
  ) +
  theme_minimal() +
  ylim(0, 5000) +
  xlim(0, 1.5)

reaction_vs_latdev_by_drive_model <-
  lmer(
    data = wideform_task_matrix,
    formula = (
      (Reaction_Frames * (1000 / 60)) ~
        Lat_Dev_SD_Control +
        KSS_cent +
        BAC +
        Road_Surface +
        as.numeric(Drive) + # To adjust for learning effect
        Lat_Dev_SD_Control * BAC +
        (1 | Subject)
    )
  )
summary(reaction_vs_latdev_by_drive_model)
```

## SDLP by task segment

```{r SDLP by task segment}
lat_dev_phase_model <- lmer(
  data = task_matrix,
  formula = Lat_Dev_SD ~
    Lat_Dev_abs_init +
    KSS_cent +
    BAC +
    BAC * KSS_cent +
    BAC * Phase +
    Road_Surface +
    as.numeric(Drive) +
    Phase +
    (1 | Subject)
)
summary(lat_dev_phase_model)
confint(lat_dev_phase_model)
plot_model(lat_dev_phase_model,
  type = "pred",
  terms = c("BAC", "KSS_cent"),
  ci.lvl = 0.95,
  axis.title = c("BrAC", "SDLP"),
  legend.title = "KSS - 5\n(median centered)",
  title = "Interaction plot: SDLP vs BrAC"
)
visreg(lat_dev_phase_model, "BAC", by = "KSS_cent", layout = c(3, 1))
```

There is strong evidence to suggest that the effect of
BAC on SDLP is lessened as KSS increases.

There is no evidence that the effect of BAC on SDLP differs by task segment
$(p > 0.6)$ for each task phase vs control.

## Lane departure logit

```{r Lane departure logit}
lane_departure_model <- glmer(
  data = task_matrix,
  formula = (
    Lane_Departure ~
      BAC +
      KSS_cent +
      Phase +
      Road_Surface +
      as.numeric(Drive) +
      (1 | Subject)
  ),
  family = "binomial"
)
summary(lane_departure_model)
```

## `Per_Close` analysis

```{r Per_Close analysis}
# Heat map
task_matrix %>%
  drop_na(Per_Close, KSS) %>%
  group_by(Drive, KSS) %>%
  summarize(
    Per_Close = median(Per_Close),
    Total_tasks = n(),
    .groups = "drop"
  ) %>%
  complete(Drive, KSS) %>%
  {
    ggplot(
      data = .,
      aes(y = factor(KSS), x = Drive)
    ) +
      geom_tile(aes(fill = Per_Close)) +
      scale_fill_gradient(
        low = "royalblue",
        high = "springgreen",
        na.value = "gray"
      ) +
      labs(
        x = "Drive",
        y = "KSS score",
        fill = "Proportion of time\nwith eyes closed"
      ) +
      coord_cartesian(expand = FALSE) +
      theme_minimal()
  }

per_close_model <- glmmTMB(
  # A single observation of Per_Close = 1,
  # not likely to be seen frequently in population data
  data = filter(task_matrix, Per_Close != 1),
  formula = (
    Per_Close ~
      KSS_cent +
      BAC +
      Phase +
      BAC * KSS_cent +
      BAC * Phase +
      Road_Surface +
      as.numeric(Drive) + # To adjust for learning effect
      (1 | Subject)
  ),
  ziformula = ~1,
  family = beta_family()
)
summary(per_close_model)
confint(per_close_model)
```

While there is no significant difference in `Per_Close` by task phase,
there is strong evidence that the effect of either KSS or BAC on `Per_Close`
is lessened as the other increases (similar to SDLP in the current model).
There is also strong evidence that `Per_Close` increases with drive, so
it's important to consider if Drive is absorbing the "fatigue effect"
that should increase `Per_Close` with both KSS and Drive.
There is no evidence of a significant BAC:Phase interaction,
but, similarly to the saccade logit model, there is more evidence of a
difference in BAC effect between control and task segments.

## Brake force analysis

```{r Brake force analysis}
brake_force_model <- lmer(
  data = task_matrix,
  formula = (
    Brake_Force_mean ~
      Phase +
      KSS_cent +
      BAC +
      BAC * Phase +
      BAC * KSS_cent +
      Road_Surface +
      as.numeric(Drive) +
      (1 | Subject)
  )
)
summary(brake_force_model)
```

Interaction terms BAC:Phase and BAC:KSS are not statistically significant.
Since changing from a three-segment to a two segment model,
the effect of BAC on brake force is no longer statistically significant.

```{r Generate visuals for paper}
generate_table(
  lat_dev_phase_model,
  "SDLP linear model"
)
generate_table(
  lane_departure_model,
  "Lane departure logit model"
)
generate_table(
  per_close_model,
  "Per Close beta model",
  shape = component + term ~ statistic,
  align = "llrcrc"
)
generate_table(
  saccade_logit_model,
  "Saccade logit model"
)

# BrAC slope by KSS score
sdlp_kss_bac_coef_plot <- emtrends(
  object = lat_dev_phase_model,
  data = task_matrix,
  specs = ~KSS_cent,
  var = "BAC",
  at = list(KSS_cent = -4:4),
  component = "cond"
) %>%
  as.data.frame() %>%
  mutate(KSS = KSS_cent + abs(min(KSS_cent)) + 1) %>%
  ggplot(aes(x = KSS, y = BAC.trend)) +
  geom_hline(yintercept = 0, color = "darkgray", linewidth = 1, linetype = 4) +
  geom_point() +
  geom_errorbar(aes(ymin = lower.CL, ymax = upper.CL), width = 1 / 3) +
  scale_x_continuous(breaks = 1:9) +
  scale_y_continuous(breaks = function(y) floor(min(y)):ceiling(max(y))) +
  labs(
    x = "KSS score",
    y = "Effect of BrAC on SDLP (95% CI)",
    title = "Effect of BrAC on SDLP by KSS score"
  )
ggsave("./output/sdlp_kss_bac_coef_plot.svg", sdlp_kss_bac_coef_plot)

# Time-series plot with tasks shaded
non_aug %>%
  filter(DaqName == non_aug[[1, "DaqName"]]) %>%
  arrange(Frame_Num) %>%
  filter(!rev(cumall(rev(Vehicle_Speed < 60)))) %>%
  mutate(Minute = (Frame_Num + 1 - min(Frame_Num)) / 3600) %>%
  {
    ggplot(data = ., aes(x = Minute, y = Vehicle_Speed)) +
      geom_line() +
      geom_rect(
        data = data.frame(
          xmin = .$Minute[match(task_boundaries$Control_Start, non_aug$X)],
          xmax = .$Minute[match(task_boundaries$Control_End, non_aug$X)]
        ),
        inherit.aes = FALSE,
        aes(
          xmin = xmin,
          xmax = xmax,
          ymin = -Inf,
          ymax = Inf,
          fill = "Control"
        ),
          alpha = 0.4
      ) +
      geom_rect(
        data = data.frame(
          xmin = .$Minute[match(task_boundaries$Task_Start, non_aug$X)],
          xmax = .$Minute[match(task_boundaries$Task_End, non_aug$X)]
        ),
        inherit.aes = FALSE,
        aes(
          xmin = xmin,
          xmax = xmax,
          ymin = -Inf,
          ymax = Inf,
          fill = "Task"
        ),
          alpha = 0.4
      ) +
      scale_fill_manual(
        name = "Segment",
        values = c(
          "Control" = "blue",
          "Task" = "red"
        )
      ) +
    labs(
      title = "Vehicle speed time series, highlighting tasks",
      x = "Minute of drive",
      y = "Vehicle speed"
    )
  } %>%
  ggsave("./output/speed_time_series_highlighted.svg", .)
```
