---
title: "Secondary Tasks Analysis"
output:
  prettydoc::html_pretty:
    theme: cayman
    highlight: github
author:
  - "John Kafumbe"
  - "Jeffrey Olsen"
date: "`r format(Sys.time(), '%B %d, %Y')`"
---

```{r setup}
#| include = FALSE

knitr::opts_chunk$set(echo = TRUE, fig.path = ".figures/")

library(tidyverse)
library(dplyr)
library(lme4)
library(glue)
library(mgcv)
library(data.table)
library(this.path)
library(glmmTMB)
library(plotly)

MAKE_PLOTS <- TRUE
```

```{r Read in data}
#| include = FALSE

setwd(this.dir())

if (file.mtime("./data/processed_data.RData") <
  file.mtime("./data_processing.R")) {
  source("./data_processing.R")
} else {
  load("./data/processed_data.RData")
}
```

## Models

```{r Models}
model_combined <- lmer(Avg_Pupil_Diameter_mean_diff ~ factor(Drive) + (1 | Subject),
  data = wideform_task_matrix
)
summary(model_combined)

# Model to compare Pupil_diff_avg in relation to press events and lane deviation events

model2 <- lmer(Deviation_Frames_Prop_Diff ~ factor(Drive) + (1 | Subject),
  data = wideform_task_matrix
)
summary(model2)

# Model testing the fixed effects of alcohol (BAC) and fatigue (KSS) on averaged bilateral pupil reactivity, controlling for individual baseline variance

model3 <- lmer(Avg_Pupil_Diameter_mean_diff ~ BAC + KSS + (1 | Subject),
  data = wideform_task_matrix
)
summary(model3)

# SDLP Model predicted by alcohol and fatigue

model_sdlp <- lmer(Lat_Dev_SD_diff ~ BAC + KSS + (1 | Subject),
  data = wideform_task_matrix
)
summary(model_sdlp)

# Speed_SD_Diff model predicted by alcohol and fatigue

model_speed <- lmer(Speed_SD_diff ~ BAC + KSS + (1 | Subject),
  data = wideform_task_matrix
)
summary(model_speed)

# Lane departure proportion difference (you already build this column)
model_dev <- lmer(Deviation_Frames_Prop_Diff ~ BAC + KSS + (1 | Subject),
  data = wideform_task_matrix
)
summary(model_dev)

print(t.test(wideform_task_matrix$Lat_Dev_SD_Post_Press - wideform_task_matrix$Lat_Dev_SD_Pre_Press))
print(t.test(wideform_task_matrix$Speed_SD_Post_Press - wideform_task_matrix$Speed_SD_Pre_Press))
```

## Preliminary lane deviation analysis

```{r Preliminary lane deviation analysis}
#| fig.show = "hide",
#| eval = MAKE_PLOTS

ggplot(
  data = filter(
    task_matrix,
    Drive == 1 & Phase == "Pre_Press"
  ),
  aes(x = Deviation_frames_prop)
) +
  geom_density() +
  geom_vline(
    aes(xintercept = mean(filter(
      task_matrix,
      Drive == 1 & Phase == "Pre_Press"
    )$Deviation_frames_prop)),
    linetype = "dashed"
  ) +
  xlim(0, 1) +
  labs(title = "Sober time deviated pre-press (as proportion)")
ggplot(
  data = filter(
    task_matrix,
    Drive == 1 & Phase == "Post_Press"
  ),
  aes(x = Deviation_frames_prop)
) +
  geom_density() +
  geom_vline(
    aes(xintercept = mean(filter(
      task_matrix,
      Drive == 1 & Phase == "Post_Press"
    )$Deviation_frames_prop)),
    linetype = "dashed"
  ) +
  xlim(0, 1) +
  labs(title = "Sober time deviated post-press (as proportion)")

ggplot(
  data = filter(
    task_matrix,
    Drive == 2 & Phase == "Pre_Press"
  ),
  aes(x = Deviation_frames_prop)
) +
  geom_density() +
  geom_vline(
    aes(xintercept = mean(filter(
      task_matrix,
      Drive == 2 & Phase == "Pre_Press"
    )$Deviation_frames_prop)),
    linetype = "dashed"
  ) +
  xlim(0, 1) +
  labs(title = "0.1 BrAC time deviated pre-press (as proportion)")
ggplot(
  data = filter(
    task_matrix,
    Drive == 2 & Phase == "Post_Press"
  ),
  aes(x = Deviation_frames_prop)
) +
  geom_density() +
  geom_vline(
    aes(xintercept = mean(filter(
      task_matrix,
      Drive == 2 & Phase == "Post_Press"
    )$Deviation_frames_prop)),
    linetype = "dashed"
  ) +
  xlim(0, 1) +
  labs(title = "0.1 BrAC time deviated post-press (as proportion)")
```

## Distributions of deviation proportion differences by drive

```{r Distributions of deviation proportion differences by drive}
#| eval = MAKE_PLOTS,
#| fig.show = "hide"

# Limit to tasks where there was at least one frame of deviation before or after
for (i in 1:5) {
  print(ggplot(
    data = wideform_task_matrix %>% filter(
      Drive == i,
      Deviation_frames_prop_Post_Press != 0 |
        Deviation_frames_prop_Pre_Press != 0
    ),
    aes(x = Deviation_Frames_Prop_Diff)
  ) +
    geom_density() +
    xlim(-1, 1) +
    labs(title = glue("Drive {i}")))
}
```

## Plots of trends across individuals

```{r Plots of trends across individuals}
#| fig.show = "hold",
#| eval = MAKE_PLOTS

# Average pupil diameter
for (i in 1:5) {
  print(ggplot(
    data = filter(non_aug, Drive == i) %>%
      group_by(Subject, Drive, Frame_Num) %>%
      mutate(Avg_Pupil_Diameter_mean = mean(Avg_Pupil_Diameter, na.rm = TRUE)) %>%
      ungroup(),
    aes(x = Frame_Num, y = Avg_Pupil_Diameter_mean, color = Subject)
  ) +
    geom_smooth(
      linewidth = 0.1,
      se = FALSE,
      method = "bam",
      formula = y ~ s(x, bs = "cs")
    ) +
    theme(legend.position = "NONE") +
    labs(title = glue("Drive {i}")))
}
```

## Box plots to compare pre & post tasks

```{r Box Plots for task matrix}
#| eval = MAKE_PLOTS

plot_data <- task_matrix %>%
  filter(Phase != "Control") %>%
  mutate(Phase = factor(Phase, levels = c("Pre_Press", "Post_Press"))) %>%
  filter(!is.na(Avg_Pupil_Diameter_mean))

ggplot(plot_data, aes(x = Phase, y = Avg_Pupil_Diameter_mean)) +
  geom_boxplot(alpha = 0.7, outlier.alpha = 0.3) +
  theme_minimal() +
  labs(title = "Pupil Dilation: Anticipation vs Reaction")
```

## Plots of trends around button presses

```{r Plots of trends around button presses}
#| eval = MAKE_PLOTS

# Get left button press indices
left_button_press_indices <- filter(non_aug, Left_Button_Press == 1)$X

# Create a list of filtered data frames
obs_around_press <- bind_rows(lapply(
  unique(task_matrix$Frame_Index),
  function(press) {
    frames_in_segment <- filter(task_matrix, Frame_Index == press)[[1, "Reaction_Frames"]]

    non_aug[seq(
      press - frames_in_segment,
      press + frames_in_segment - 1
    ), ] %>%
      mutate(
        Press_Frame = press,
        Frame_in_Segment = X - press + frames_in_segment + 1,
        Adj_Frame_in_Segment = -100 +
          (((Frame_in_Segment - min(Frame_in_Segment)) * 200) /
            (max(Frame_in_Segment) - min(Frame_in_Segment)))
      )
  }
))

plot_metric_around_task <- function(variable, ymin, ymax, subject) {
  ggplot(
    data = filter(
      obs_around_press,
      Subject == subject,
    ),
    aes(
      x = Adj_Frame_in_Segment,
      y = .data[[variable]],
      color = factor(Press_Frame),
    )
  ) +
    geom_line(linewidth = 0.1) +
    theme(legend.position = "NONE") +
    geom_vline(xintercept = 0, linewidth = 1) +
    labs(
      title = glue("All button presses: Subject {subject}"),
      x = "Time (relative to press)",
      y = variable
    ) +
    ylim(ymin, ymax) +
    facet_wrap(~Drive, ncol = 2, scales = "free")
}

metrics <- list(
  list(variable = "Avg_Pupil_Diameter", ymin = 0, ymax = 6),
  list(variable = "Vehicle_Lat_Dev", ymin = -6, ymax = 6)
)
for (metric in metrics) {
  print(plot_metric_around_task(metric$variable, metric$ymin, metric$ymax, 1))
}
```

Interpretability relies on the assumption that trends in eye metrics
change faster/slower proportional to the task reaction time.

## Pupil diameter by KSS and drive

```{r Pupil diameter by KSS and drive}
#| fig.show = "hold",
#| eval = MAKE_PLOTS
eye_kss <- non_aug %>%
  filter(!is.na(Avg_Pupil_Diameter) & !is.na(KSS_Score)) %>%
  select(KSS_Score, Frame_Num, Drive, Avg_Pupil_Diameter) %>%
  group_by(KSS_Score, Frame_Num, Drive) %>%
  summarize(
    Avg_Pupil_Diameter = mean(Avg_Pupil_Diameter),
    .groups = "drop"
  )

for (i in 1:5) {
  print(ggplot(
    data = filter(eye_kss, Drive == i),
    aes(
      x = Frame_Num,
      y = Avg_Pupil_Diameter,
      group = factor(KSS_Score),
      color = as.numeric(as.character(KSS_Score))
    )
  ) +
    geom_smooth(
      linewidth = 0.3, se = FALSE,
      method = "bam", formula = y ~ s(x, bs = "cs")
    ) +
    theme(legend.position = "bottom") +
    scale_color_viridis_c(name = "KSS", direction = -1) +
    labs(title = glue("Drive {i}"))) +
    ylim(0, 6)
}
```

## Reaction time by subject, drive, KSS

```{r "Reaction time by subject, drive, KSS"}
#| eval = MAKE_PLOTS

task_matrix %>%
  drop_na(KSS, Subject, Drive, Reaction_Frames) %>%
  group_by(Subject, Drive, KSS) %>%
  summarize(
    Reaction_Time = mean(Reaction_Frames) * (1000 / 60),
    .groups = "drop"
  ) %>%
  {
    # Line plot
    print(
      ggplot(
        data = filter(
          .,
          as.numeric(Subject) %in% sample(
            unique(task_matrix$Subject),
            10
          )
        ),
        aes(x = Drive, y = Reaction_Time, group = Subject)
      ) +
        geom_point(aes(color = KSS), size = 3) +
        geom_line() +
        labs(x = "Drive", y = "Reaction time (ms)", color = "KSS score")
    )
  }
task_matrix %>%
  group_by(Drive, KSS) %>%
  summarize(
    Reaction_Time = mean(Reaction_Frames) * (1000 / 60),
    Total_tasks = n(),
    .groups = "drop"
  ) %>%
  {
    # Heat map
    ggplotly(
      ggplot(
        data = .,
        aes(y = factor(KSS), x = Drive)
      ) +
        geom_tile(aes(fill = Reaction_Time)) +
        scale_fill_gradient(low = "royalblue", high = "springgreen") +
        labs(x = "Drive", y = "KSS score", fill = "Reaction time (ms)")
    )
  }
task_matrix %>%
  mutate(Reaction_Time = Reaction_Frames * (1000 / 60)) %>%
  {
    # Box plot
    print(
      ggplot(
        data = .,
        aes(x = factor(KSS), y = Reaction_Time)
      ) +
        geom_boxplot(outlier.shape = NA) +
        facet_wrap(~Drive) +
        ylim(0, 4000) +
        labs(x = "KSS score", y = "Reaction time (ms)")
    )
  }
```

Currently samples 10 drivers. In the future we could group them by
some trait and aggregate across drivers within groups.

## Zero-inflated poisson model for saccades

```{r Saccade Zero Inflation}
#| out.width = "100%",
#| eval = MAKE_PLOTS

task_matrix %>%
  group_by(Phase) %>%
  summarise(
    prop_zero = mean(Saccade_Count == 0),
    mean_count = mean(Saccade_Count),
    median_count = median(Saccade_Count)
  )
ggplot(task_matrix, aes(x = Saccade_Count)) +
  geom_histogram(binwidth = 0.5) +
  facet_wrap(~Phase)

model_saccade_zip <- glmmTMB(
  Saccade_Count ~ Phase + BAC + KSS + (1 | Subject),
  ziformula = ~ Phase + BAC, # What predicts being in the "zero" group?
  family = poisson,
  data = task_matrix
)

summary(model_saccade_zip)
```

```{r Visualization for zero-saccade windows by Drive}
task_matrix %>%
  mutate(Zero_Saccade = Saccade_Count == 0) %>%
  group_by(Drive, Phase) %>%
  summarise(
    Prop_Zero = mean(Zero_Saccade),
    SE = sd(Zero_Saccade) / sqrt(n()),
    .groups = "drop"
  ) %>%
  ggplot(aes(x = factor(Drive), y = Prop_Zero, fill = Phase)) +
  geom_col(position = "dodge") +
  theme_minimal()
```
```{r Pre press Driving Stability and Reaction Time Plot and model}
#| out.width = "100%"

model_rt_driving <- lmer(
  Reaction_Frames_Pre_Press ~ Lat_Dev_SD_Pre_Press + Speed_SD_Pre_Press + BAC + KSS + (1 | Subject),
  data = wideform_task_matrix
)
summary(model_rt_driving)

wideform_task_matrix %>%
  drop_na(Lat_Dev_SD_Pre_Press, Reaction_Frames_Pre_Press, Drive, KSS) %>%
  mutate(Drive = factor(Drive, labels = c("Drive 1", "Drive 2", "Drive 3", "Drive 4", "Drive 5"))) %>%
  ggplot(aes(x = Lat_Dev_SD_Pre_Press, y = Reaction_Frames_Pre_Press * (1000 / 60), color = KSS)) +
  geom_point(alpha = 0.3, size = 1.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black", linewidth = 0.5) +
  scale_color_viridis_c(direction = -1) +
  facet_wrap(~Drive) +
  labs(
    x = "Lateral deviation SD before press (m)",
    y = "Reaction time (ms)",
    color = "KSS",
    title = "Pre-press driving stability vs reaction time",
  ) +
  theme_minimal()
```
