---
title: "Secondary Tasks Analysis"
output:
  rmdformats::html_clean:
    highlight: espresso
    lib_dir: ".libs/"
    toc: true
author:
  - "John Kafumbe"
  - "Jeffrey Olsen"
date: "`r format(Sys.time(), '%B %d, %Y')`"
---

```{r setup}
#| include = FALSE

knitr::opts_chunk$set(
  echo = TRUE,
  cache = TRUE,
  autodep = TRUE,
  fig.path = ".figures/",
  cache.path = ".cache/",
  fig.width = 7,
  fig.height = 5,
  dev = "svglite"
)

library(tidyverse)
library(lme4)
library(lmerTest)
library(glue)
library(mgcv)
library(this.path)
library(glmmTMB)
library(sjPlot)
library(performance)
library(visreg)
library(modelsummary)
library(emmeans)
library(ggbreak)
library(qs2)
library(downloadthis)
library(knitr)
library(tableone)
library(rsvg)
library(patchwork)
library(ggplotify)
library(broom.mixed)
library(kableExtra)

dir.create("./output", showWarnings = FALSE)

# ggplot options
theme_set(theme_bw())
palette.colors(palette = "Okabe-Ito") %>%
  c(
    "Control" = .[3],
    "180" = .[3],
    "3s" = .[3],
    "Task" = .[2],
    "300" = .[2],
    "5s" = .[2],
    "600" = .[4],
    "10s" = .[4]
  ) %>%
  {
    options(
      ggplot2.discrete.colour = .,
      ggplot2.discrete.fill = .
    )
  }
```

<div style="text-align: center;">
```{r Download Rmd}
#| echo = FALSE

download_file(
  this.path(),
  button_label = "Download Rmd",
  button_type = "primary",
  has_icon = TRUE,
  self_contained = TRUE
)
```
</div>

```{r Read in data}
#| cache = FALSE,
#| include = FALSE

setwd(this.dir())

if (!file.exists("./data/final_data.qs") |
  file.mtime("./data/final_data.qs") <
    file.mtime("./modeling.R")) {
  cat("\nGenerating models, script updated since last run.\n", file = stderr())
  source("./modeling.R")
}
qs_readm("./data/final_data.qs")
```

```{r Helpers}
#| include = FALSE

generate_table <- function(
  model_list,
  title,
  label,
  shape = term ~ model,
  align = "lrrr",
  additional_note = NULL,
  ...
) {
  modelsummary(
    model_list,
    ...,
    title = glue("{title}\\label{{{label}}}"),
    output = "latex",
    stars = TRUE,
    shape = shape,
    estimate = "{estimate}{stars}",
    statistic = c("conf.int", "p.value"),
    align = align,
    coef_rename = c(
      "(Intercept)" = "Intercept",
      "BAC" = "BrAC",
      "KSS_cent" = "KSS (median-centered)",
      "PhaseTask" = "Phase (Task)",
      "Road_SurfacePaved" = "Road surface (Paved)",
      "as.numeric(Drive)" = "Drive \\#",
      "SD (Intercept Subject)" = "Subject baseline SD",
      "SD (Intercept Frame_Index)" = "Unique task baseline SD",
      "Lat_Dev_abs_init" = "Initial lateral deviation",
      "KSS_cent:BAC" = "KSS (median-centered):BrAC",
      "BAC:KSS_cent" = "BrAC:KSS (median-centered)",
      "BAC:PhaseTask" = "BrAC:Phase (Task)",
      "PhaseTask:BAC" = "Phase (Task):BrAC",
      "Lat_Dev_SD_Control:BAC" = "Baseline SDLP:BrAC",
      "BAC:Lat_Dev_SD_Control" = "BrAC:Baseline SDLP"
    ),
    gof_omit = ".*",
    escape = FALSE,
    notes = list(
      paste(
        c(
          "+ p < 0.1, * p < 0.05, ** p < 0.01, *** p < 0.001.\\\\",
          "95\\% confidence intervals are in brackets.",
          "BrAC is reported in units of 0.01 g/dL.",
          additional_note
        ),
        collapse = " "
      )
    )
  ) %>%
    as.character() %>%
    str_replace_all(
      c(
        "\\\\begin\\{table\\}" = "\\\\begin{table}\n\\\\small",
        "component(?!s are reported)" = "Component",
        "conditional" = "Conditional",
        "zero_inflated" = "Zero-inflated",
        "dispersion" = "Dispersion",
        " 0\\." = " .",
        "-0\\." = "-.",
        "<0\\." = "<."
      )
    ) %>%
    write_lines(glue("./output/{str_replace_all(title, ' ', '_')}.tex"))
}

gen_interact_plot_kss_bac <- function(xlab, ylab, model_name, ystretch = 1) {
  lapply(
    c(180, 300, 600),
    function(x) {
      emtrends(
        object = models[[model_name]][[as.character(x)]],
        data = get(glue("task_matrix_{x}")),
        specs = ~KSS_cent,
        var = "BAC",
        at = list(KSS_cent = -4:4),
        component = "cond"
      ) %>%
        as.data.frame() %>%
        rename(any_of(c(lower.CL = "asymp.LCL", upper.CL = "asymp.UCL"))) %>%
        mutate(
          # Just transforming KSS_cent back into raw KSS
          KSS = KSS_cent + abs(min(KSS_cent)) + 1,
          # Shifting estimates to other units
          across(c(BAC.trend, lower.CL, upper.CL), ~ .x * ystretch),
          # Segment length for coloring
          `Segment length` = glue("{x / 60}s")
        )
    }
  ) %>%
    bind_rows() %>%
    # Make sure order is correct in legend
    mutate(`Segment length` = factor(
      `Segment length`,
      levels = c("3s", "5s", "10s")
    )) %>%
    ggplot(aes(x = KSS, y = BAC.trend, color = `Segment length`)) +
    geom_hline(
      yintercept = 0,
      color = "darkgray",
      linewidth = 1,
      linetype = 2
    ) +
    geom_point(position = position_dodge(width = 1 / 3)) +
    geom_errorbar(
      aes(ymin = lower.CL, ymax = upper.CL),
      width = 1 / 3,
      position = position_dodge(width = 1 / 3)
    ) +
    scale_x_continuous(breaks = 1:9) +
    labs(
      x = xlab,
      y = ylab,
      color = "Segment\nlength"
    ) +
    theme(legend.title = element_text(hjust = 1 / 2))
}
```

## Preliminary models

```{r Preliminary models}
# Background on whether treatment (not the control)
# show an association between BrAC and KSS
non_aug %>%
  group_by(DaqName) %>%
  slice(1) %>%
  ungroup() %>%
  filter(Drive != 1) %>%
  ggplot(aes(x = Start_BAC, y = KSS_Score)) +
  geom_point() +
  labs(
    x = "BrAC",
    y = "KSS",
    title = "Fatigue vs impairment across dosed drives"
  ) +
  geom_smooth(method = "lm", se = TRUE)

# Model uses BrAC units of 0.01 g/dL
summary(models[["bac_kss"]])

# Model testing the fixed effects of alcohol (BAC) and fatigue (KSS) on
# averaged bilateral pupil reactivity,
# controlling for individual baseline variance
lapply(models[["pup"]], summary)

# SDLP Model predicted by alcohol and fatigue
lapply(models[["sdlp"]], summary)

# Speed_SD_Diff model predicted by alcohol and fatigue
lapply(models[["speed"]], summary)

# Lane departure proportion difference
lapply(models[["dev"]], summary)

for (metric in c(
  "Avg_Pupil_Diameter_mean_diff",
  "Lat_Dev_SD_diff",
  "Speed_SD_diff",
  "Per_Close_diff",
  "Brake_Force_mean_diff"
)) {
  for (val in c(180, 300, 600)) {
    print(glue("{metric}: {val / 60} second segments"))
    print(
      as.vector(
        t.test(
          get(
            glue("wideform_task_matrix_{val}")
          )[[metric]]
        )$conf.int
      )
    )
    cat("\n")
  }
}
rm(metric, val)
```

## Preliminary lane deviation analysis

```{r Preliminary lane deviation analysis}
#| fig.height = 10,
#| out.width = "100%"

ggplot(
  data = task_matrix_180,
  aes(x = Deviation_Frames_prop)
) +
  geom_density() +
  geom_vline(
    aes(xintercept = mean(filter(
      task_matrix_180,
      Drive == 1 & Phase == "Control"
    )$Deviation_Frames_prop)),
    linetype = "dashed"
  ) +
  facet_wrap(~ Drive + Phase, ncol = 2) +
  xlim(0, 1)
```

## Distributions of deviation proportion differences by drive

```{r Distributions of deviation proportion differences by drive}
# Limit to tasks where there was at least one frame of deviation before or after
ggplot(
  data = wideform_task_matrix_180 %>% filter(
    Deviation_Frames_prop_Task != 0 |
      Deviation_Frames_prop_Control != 0
  ),
  aes(x = Deviation_Frames_prop_diff)
) +
  geom_density() +
  facet_wrap(~Drive) +
  xlim(-1, 1)
```

## Plots of trends across individuals

```{r Plots of trends across individuals}
#| fig.show = "hold"

# Average pupil diameter
ggplot(
  data = non_aug %>%
    group_by(Subject, Drive, Frame_Num) %>%
    mutate(Avg_Pupil_Diameter_mean = mean(
      Avg_Pupil_Diameter,
      na.rm = TRUE
    )) %>%
    ungroup(),
  aes(x = Frame_Num, y = Avg_Pupil_Diameter_mean, color = Subject)
) +
  geom_smooth(
    linewidth = 0.1,
    se = FALSE,
    method = "bam",
    formula = y ~ s(x, bs = "cs")
  ) +
  facet_wrap(~Drive) +
  theme(legend.position = "NONE")
```

## Box plots to compare control & task phases

```{r Box Plots for task matrix}
task_matrix_180 %>%
  filter(!is.na(Avg_Pupil_Diameter_mean)) %>%
  ggplot(aes(x = Phase, y = Avg_Pupil_Diameter_mean)) +
  geom_boxplot(alpha = 0.7, outlier.alpha = 0.3) +
  theme_minimal() +
  labs(title = "Pupil Dilation: Anticipation vs Reaction")
```

## Plots of trends around button presses

```{r Plots of trends around button presses}
# Get left button press indices
# left_button_press_indices <- filter(non_aug, Left_Button_Press == 1)$X

# Create a list of filtered data frames
obs_around_press <- bind_rows(lapply(
  unique(task_matrix_180$Frame_Index),
  function(press) {
    frames_in_segment <- filter(
      task_matrix_180,
      Frame_Index == press
    )[[1, "Reaction_Frames"]]

    non_aug[seq(
      press - frames_in_segment,
      press + frames_in_segment - 1
    ), ] %>%
      mutate(
        Press_Frame = press,
        Frame_in_Segment = X - press + frames_in_segment + 1,
        Adj_Frame_in_Segment = -100 +
          (((Frame_in_Segment - min(Frame_in_Segment)) * 200) /
            (max(Frame_in_Segment) - min(Frame_in_Segment)))
      )
  }
))

plot_metric_around_task <- function(variable, ymin, ymax, subject) {
  ggplot(
    data = filter(
      obs_around_press,
      Subject == subject,
    ),
    aes(
      x = Adj_Frame_in_Segment,
      y = .data[[variable]],
      color = factor(Press_Frame),
    )
  ) +
    geom_line(linewidth = 0.1) +
    theme(legend.position = "NONE") +
    geom_vline(xintercept = 0, linewidth = 1) +
    labs(
      title = glue("All button presses: Subject {subject}"),
      x = "Time (relative to press)",
      y = variable
    ) +
    ylim(ymin, ymax) +
    facet_wrap(~Drive, ncol = 2, scales = "free")
}

metrics <- list(
  list(variable = "Avg_Pupil_Diameter", ymin = 0, ymax = 6),
  list(variable = "Vehicle_Lat_Dev", ymin = -6, ymax = 6)
)
for (metric in metrics) {
  print(plot_metric_around_task(metric$variable, metric$ymin, metric$ymax, 1))
}
rm(metric, metrics, obs_around_press, plot_metric_around_task)
```

Interpretability relies on the assumption that trends in eye metrics
change faster/slower proportional to the task reaction time.

## Pupil diameter by KSS and drive

```{r Pupil diameter by KSS and drive}
non_aug %>%
  filter(!is.na(Avg_Pupil_Diameter) & !is.na(KSS_Score)) %>%
  select(KSS_Score, Frame_Num, Drive, Avg_Pupil_Diameter) %>%
  group_by(KSS_Score, Frame_Num, Drive) %>%
  summarize(
    Avg_Pupil_Diameter = mean(Avg_Pupil_Diameter),
    .groups = "drop"
  ) %>%
  ggplot(
    aes(
      x = Frame_Num,
      y = Avg_Pupil_Diameter,
      group = factor(KSS_Score),
      color = as.numeric(as.character(KSS_Score))
    )
  ) +
  geom_smooth(
    linewidth = 0.3, se = FALSE,
    method = "bam", formula = y ~ s(x, bs = "cs")
  ) +
  facet_wrap(~Drive) +
  theme(legend.position = "bottom") +
  scale_color_viridis_c(name = "KSS", direction = -1) +
  ylim(0, 6)

lapply(models[["pupil_diameter_diff"]], summary)
lapply(models[["pupil_diameter_diff"]], check_collinearity)
```

## Reaction time by subject, drive, KSS

```{r "Reaction time by subject, drive, KSS"}
#| out.width = "100%"

# Line plot
task_matrix_180 %>%
  drop_na(KSS, Subject, Drive, Reaction_Frames) %>%
  group_by(Subject, Drive, KSS) %>%
  summarize(
    Reaction_Time = mean(Reaction_Frames) * (1000 / 60),
    .groups = "drop"
  ) %>%
  {
    ggplot(
      data = filter(
        .,
        as.numeric(Subject) %in% sample(
          unique(task_matrix_180$Subject),
          10
        )
      ),
      aes(x = Drive, y = Reaction_Time, group = Subject)
    ) +
      geom_point(aes(color = KSS), size = 3) +
      geom_line() +
      labs(x = "Drive", y = "Reaction time (ms)", color = "KSS score") +
      scale_color_continuous(breaks = 1:9, limits = c(1, 9))
  }

# Heat map
task_matrix_180 %>%
  drop_na(KSS) %>%
  group_by(Drive, KSS) %>%
  summarize(
    Reaction_Time = median(Reaction_Frames) * (1000 / 60),
    Total_tasks = n(),
    .groups = "drop"
  ) %>%
  complete(KSS, Drive) %>%
  {
    ggplot(
      data = .,
      aes(y = factor(KSS), x = Drive)
    ) +
      geom_tile(aes(fill = Reaction_Time)) +
      scale_fill_gradient(
        low = "royalblue",
        high = "springgreen",
        na.value = "gray"
      ) +
      coord_cartesian(expand = FALSE) +
      theme_minimal() +
      labs(x = "Drive", y = "KSS score", fill = "Reaction time (ms)")
  }

# Box plot
wideform_task_matrix_180 %>%
  mutate(Reaction_Time = Reaction_Frames * (1000 / 60)) %>%
  drop_na(Phase_Control, KSS) %>%
  {
    ggplot(
      data = .,
      aes(x = factor(KSS), y = Reaction_Time)
    ) +
      geom_boxplot(outlier.shape = NA) +
      facet_wrap(~Drive) +
      ylim(0, 4000) +
      labs(x = "KSS score", y = "Reaction time (ms)")
  }
```

Currently samples 10 drivers. In the future we could group them by
some trait and aggregate across drivers within groups.

## Saccades ZIP model

```{r Saccades ZIP model}
#| out.width = "100%"

ggplot(task_matrix_180, aes(x = Saccade_Count)) +
  geom_histogram(binwidth = 0.5) +
  facet_wrap(~Phase)

lapply(models[["saccade_zip"]], summary)
```

## Saccade binary visualizations

```{r Saccade binary visualizations}
task_matrix_180 %>%
  mutate(Zero_Saccade = Saccade_Count == 0) %>%
  group_by(Drive, Phase) %>%
  summarize(
    Prop_Zero = mean(Zero_Saccade),
    SE = sd(Zero_Saccade) / sqrt(n()),
    .groups = "drop"
  ) %>%
  ggplot(aes(
    x = factor(Drive),
    y = Prop_Zero,
    fill = factor(Phase,
      labels = c(
        "Control",
        "Task"
      )
    )
  )) +
  geom_col(position = "dodge") +
  labs(
    x = "Drive",
    y = "Proportion of segments with zero saccades",
    fill = "Phase"
  ) +
  theme_minimal()
```

## Saccade logit

```{r Saccade logit}
lapply(models[["saccade_logit"]], summary)
```

## Reaction time by SDLP prior to task

```{r Reaction time by SDLP prior to task}
#| out.width = "100%"

lapply(models[["rt_driving"]], summary)

wideform_task_matrix_180 %>%
  drop_na(Lat_Dev_SD_Control, Reaction_Frames, Drive, KSS) %>%
  mutate(Drive = factor(
    Drive,
    labels = c(
      "Drive 1",
      "Drive 2",
      "Drive 3",
      "Drive 4",
      "Drive 5"
    )
  )) %>%
  ggplot(aes(
    x = Lat_Dev_SD_Control,
    y = Reaction_Frames * (1000 / 60),
    color = KSS
  )) +
  geom_point(alpha = 0.3, size = 1.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black", linewidth = 0.5) +
  scale_color_viridis_c(direction = -1) +
  facet_wrap(~Drive) +
  labs(
    x = "Lateral deviation SD before press (ft)",
    y = "Reaction time (ms)",
    color = "KSS",
    title = "Control frame driving stability vs reaction time",
  ) +
  theme_minimal() +
  ylim(0, 5000) +
  xlim(0, 1.5)

lapply(models[["reaction_vs_latdev_by_drive"]], summary)
```

## SDLP by task segment

```{r SDLP by task segment}
lapply(models[["lat_dev_phase"]], summary)
lapply(
  models[["lat_dev_phase"]],
  function(model) {
    plot_model(
      model,
      type = "pred",
      terms = c("BAC", "KSS_cent"),
      ci.lvl = 0.95,
      axis.title = c("BrAC", "SDLP"),
      legend.title = "KSS - 5\n(median centered)",
      title = "Interaction plot: SDLP vs BrAC"
    ) + scale_x_continuous(labels = function(x) x / 100)
  }
)
lapply(
  models[["lat_dev_phase"]],
  function(model) {
    plot_model(
      model,
      type = "pred",
      terms = c("BAC", "Phase"),
      ci.lvl = 0.95,
      axis.title = c("BrAC", "Phase"),
      legend.title = "Segment type",
      title = "Interaction plot: SDLP vs Phase"
    ) + scale_x_continuous(labels = function(x) x / 100)
  }
)
lapply(
  models[["lat_dev_phase_visreg"]],
  function(x) {
    print(
      plot(
        x,
        layout = c(3, 1),
        gg = TRUE
      ) + scale_x_continuous(labels = function(x) x / 100)
    )
  }
)
```

## Lane departure logit

```{r Lane departure logit}
lapply(models[["lane_departure"]], summary)
```

## Vehicle speed LMMs

```{r Vehicle speed LMMs}
lapply(models[["speed_sd"]], summary)
lapply(models[["speed_mean"]], summary)
```

## Reaction time LMM

```{r Reaction time LMM}
summary(models[["reaction_time"]])
```

## `Per_Close` analysis

```{r Per_Close analysis}
# Heat map
task_matrix_180 %>%
  drop_na(Per_Close, KSS) %>%
  group_by(Drive, KSS) %>%
  summarize(
    Per_Close = median(Per_Close),
    Total_tasks = n(),
    .groups = "drop"
  ) %>%
  complete(Drive, KSS) %>%
  {
    ggplot(
      data = .,
      aes(y = factor(KSS), x = Drive)
    ) +
      geom_tile(aes(fill = Per_Close)) +
      scale_fill_gradient(
        low = "royalblue",
        high = "springgreen",
        na.value = "gray"
      ) +
      labs(
        x = "Drive",
        y = "KSS score",
        fill = "Proportion of time\nwith eyes closed"
      ) +
      coord_cartesian(expand = FALSE) +
      theme_minimal()
  }

# Coefficients plot
imap_dfr(models[["per_close"]], function(m, frames) {
  tidy(m,
    effects = "fixed", component = "cond",
    conf.int = TRUE, exponentiate = TRUE
  ) %>%
    mutate(Window = glue("{as.numeric(frames) / 60}s"))
}) %>%
  filter(term != "(Intercept)") %>%
  ggplot(aes(x = estimate, y = term, color = Window)) +
  geom_vline(xintercept = 1, linetype = "dashed", color = "darkgray") +
  geom_pointrange(
    aes(xmin = conf.low, xmax = conf.high),
    position = position_dodge(width = 0.5)
  ) +
  scale_x_log10() +
  labs(x = "Odds ratio (95% CI, log scale)", y = NULL)

lapply(
  models[["per_close"]],
  function(model) {
    plot_model(
      model,
      type = "pred",
      terms = c("BAC", "Phase"),
      ci.lvl = 0.95,
      axis.title = c("BrAC", "Phase"),
      legend.title = "Segment type",
      title = "Interaction plot: Per Close vs Phase"
    ) + scale_x_continuous(labels = function(x) x / 100)
  }
)
lapply(
  models[["per_close_80"]],
  function(model) {
    plot_model(
      model,
      type = "pred",
      terms = c("BAC", "Phase"),
      ci.lvl = 0.95,
      axis.title = c("BrAC", "Phase"),
      legend.title = "Segment type",
      title = "Interaction plot: Per Close (PM80) vs Phase"
    ) + scale_x_continuous(labels = function(x) x / 100)
  }
)

lapply(models[["per_close"]], summary)
lapply(models[["per_close_80"]], summary)
```

## Brake force analysis

```{r Brake force analysis}
lapply(models[["brake_force"]], summary)
```

```{r Generate tables for paper}
#| include = FALSE

renamed_models <- function(model) {
  setNames(
    models[[model]],
    lapply(
      as.numeric(names(models[[model]])) / 60,
      function(x) {
        glue("{x}s")
      }
    )
  )
}

generate_table(
  renamed_models("speed_sd"),
  "SDS linear model",
  "tab:sds_table"
)
generate_table(
  renamed_models("lat_dev_phase"),
  "SDLP linear model",
  "tab:sdlp_table"
)
generate_table( # Not used in paper
  renamed_models("lane_departure"),
  "Lane departure logit model",
  "tab:lane_dep_table"
)
generate_table(
  list("Reaction Time" = models[["reaction_time"]]),
  "Reaction time linear model",
  "tab:rt_table",
  align = "lr",
  additional_note = "Reaction time is reported in ms."
)
generate_table(
  renamed_models("per_close"),
  "PERCLOS beta model",
  "tab:perclos_table",
  shape = component + term ~ model,
  align = "llrrr",
  exponentiate = TRUE,
  additional_note = "Estimates are reported as odds ratios (OR)."
)
generate_table(
  renamed_models("per_close_80"),
  "PERCLOS (PM80) beta model",
  "tab:perclos80_table",
  shape = component + term ~ model,
  align = "llrrr",
  exponentiate = TRUE,
  additional_note = "Estimates are reported as odds ratios (OR)."
)
generate_table( # Not used in paper
  renamed_models("saccade_logit"),
  "Saccade logit model",
  "tab:saccade_logit_table"
)
generate_table(
  renamed_models("saccade_zip"),
  "Saccade ZIP model",
  "tab:saccade_zip_table",
  shape = component + term ~ model,
  align = "llrrr",
  exponentiate = TRUE,
  additional_note = paste(
    "Estimates for the count components are reported as",
    "incidence rate ratios (IRR).",
    "Estimates for the zero-inflated components",
    "are reported as odds ratios (OR)."
  )
)
rm(renamed_models)

bind_rows(
  mutate(task_matrix_180, Segment_Length = factor("3s", levels = c("3s", "5s", "10s"))),
  mutate(task_matrix_300, Segment_Length = factor("5s", levels = c("3s", "5s", "10s"))),
  mutate(task_matrix_600, Segment_Length = factor("10s", levels = c("3s", "5s", "10s")))
) %>%
  mutate(
    Phase = factor(Phase, levels = c("Control", "Task"))
  ) %>%
  select(
    c(
      Avg_Pupil_Diameter_mean,
      Lat_Dev_SD,
      Speed_SD,
      Brake_Force_mean,
      Saccade_Count,
      Per_Close,
      Phase,
      Segment_Length
    )
  ) %>%
  rename(
    "Mean pupil diameter (mm)" = Avg_Pupil_Diameter_mean,
    "PERCLOS" = Per_Close,
    "SDLP (ft)" = Lat_Dev_SD,
    "SDS (mph)" = Speed_SD,
    "Mean brake force" = Brake_Force_mean,
    "Saccade count" = Saccade_Count
  ) %>%
  CreateTableOne(
    strata = c("Phase", "Segment_Length"),
    vars = setdiff(names(.), c("Phase", "Segment_Length")),
    data = .
  ) %>%
  print(
    showAllLevels = FALSE,
    printToggle = FALSE,
    test = FALSE,
    explain = FALSE
  ) %>%
  .[-1, ] %>%
  apply(2, function(x) str_replace_all(x, "\\(\\s+", "(")) %>%
  {
    colnames(.) <- rep(c("Control", "Task"), 3)
    .
  } %>%
  kable(
    format = "latex",
    booktabs = TRUE,
    align = "lrrrrrr",
    linesep = "",
    caption = "Control/task summary statistics by segment length",
    label = "summary_stats_table_ext"
  ) %>%
  add_header_above(c(" " = 1, "3s" = 2, "5s" = 2, "10s" = 2)) %>%
  str_remove("\\\\toprule\n") %>%
  str_replace_all(
    c(
      "\\\\begin\\{tabular\\}" = paste(
        "\\\\resizebox{\\\\linewidth}{!}{",
        "\\\\begin{tabular}"
      ),
      "\\\\end\\{tabular\\}" = "\\\\end{tabular}}",
      "\\\\bottomrule" = paste(
        "\\\\bottomrule\n\\\\multicolumn{7}{l}{\\\\footnotesize",
        "Statistics reported are means with standard",
        "deviations in parentheses.}"
      )
    )
  ) %>%
  write_lines("./output/summary_stats_table_ext.tex")

# Simple table one with sample size, tasks, and demographic data
enframe(
  read.csv("./data/subject_drive_info.csv") %>%
    distinct(subject_id, .keep_all = TRUE) %>%
    {
      l <- nrow(.)
      disp <- function(data) {
        glue("{data} ({round(data / l * 100, 1)}\\%)")
      }
      list(
        "No. of tasks" = nrow(wideform_task_matrix_180),
        "No. of subjects" = length(unique(task_matrix_180$Subject)),
        "Sex" = "",
        "\\hspace{1em}Female" = disp(tally(., sex == "Female")),
        "\\hspace{1em}Male" = disp(tally(., sex == "Male")),
        "Race" = "",
        "\\hspace{1em}White" = disp(tally(., str_detect(race, "White"))),
        "\\hspace{1em}Asian or Asian American" = disp(
          tally(
            .,
            str_detect(race, "Asian or Asian American")
          )
        ),
        "\\hspace{1em}Black or African American" = disp(
          tally(
            .,
            str_detect(race, "Black or African American")
          )
        ),
        "\\hspace{1em}More than one race" = disp(
          tally(
            .,
            str_detect(race, "More than one race")
          )
        ),
        "\\hspace{1em}Prefer not to answer" = disp(
          tally(
            .,
            str_detect(race, "Prefer not to answer")
          )
        ),
        "Hispanic" = "",
        "\\hspace{1em}Yes" = disp(tally(., hispanic_plus == "Yes")),
        "\\hspace{1em}No" = disp(tally(., hispanic_plus == "No"))
      )
    },
  name = "Attribute",
  value = "Count"
) %>%
  kable(
    caption = glue("Summary counts"),
    format = "latex",
    escape = FALSE,
    linesep = "",
    label = "table_one"
  ) %>%
  write_lines("./output/table_one.tex")
```

## Generate visuals for paper

```{r Generate visuals for paper}
#| echo = FALSE,
#| message = FALSE


# BrAC slope by KSS score
sdlp_kss_bac_coef_plot <- gen_interact_plot_kss_bac(
  "KSS score",
  "Effect of BrAC on SDLP (cm per 0.01 g/dL, 95% CI)",
  "lat_dev_phase",
  30.48
)
ggsave("./output/sdlp_kss_bac_coef_plot.svg", sdlp_kss_bac_coef_plot)
rsvg_pdf(
  "./output/sdlp_kss_bac_coef_plot.svg",
  "./output/sdlp_kss_bac_coef_plot.pdf"
)
print(sdlp_kss_bac_coef_plot)

perclos_kss_bac_coef_plot <- gen_interact_plot_kss_bac(
  "KSS score",
  "Effect of BrAC on PERCLOS (% change per 0.01 g/dL, 95% CI)",
  "per_close",
  ystretch = 100
)
ggsave("./output/perclos_kss_bac_coef_plot.svg", perclos_kss_bac_coef_plot)
rsvg_pdf(
  "./output/perclos_kss_bac_coef_plot.svg",
  "./output/perclos_kss_bac_coef_plot.pdf"
)
print(perclos_kss_bac_coef_plot)

sds_kss_bac_coef_plot <- gen_interact_plot_kss_bac(
  "KSS score",
  "Effect of BrAC on SDS (mph per 0.01 g/dL, 95% CI)",
  "speed_sd"
)
ggsave("./output/sds_kss_bac_coef_plot.svg", sds_kss_bac_coef_plot)
rsvg_pdf(
  "./output/sds_kss_bac_coef_plot.svg",
  "./output/sds_kss_bac_coef_plot.pdf"
)
print(sds_kss_bac_coef_plot)

# Time-series plot with tasks shaded
wide_plot <- non_aug %>%
  filter(DaqName == non_aug[[1, "DaqName"]]) %>%
  arrange(Frame_Num) %>%
  filter(!rev(cumall(rev(Vehicle_Speed < 60)))) %>%
  mutate(Minute = (Frame_Num + 1 - min(Frame_Num)) / 3600) %>%
  {
    ggplot(data = ., aes(x = Minute, y = Vehicle_Speed)) +
      geom_line() +
      geom_rect(
        data = data.frame(
          xmin = .$Minute[match(task_boundaries_180$Control_Start, non_aug$X)],
          xmax = .$Minute[match(task_boundaries_180$Control_End, non_aug$X)]
        ),
        inherit.aes = FALSE,
        aes(
          xmin = xmin,
          xmax = xmax,
          ymin = -Inf,
          ymax = Inf,
          fill = "Control"
        ),
        alpha = 0.4
      ) +
      geom_rect(
        data = data.frame(
          xmin = .$Minute[match(task_boundaries_180$Task_Start, non_aug$X)],
          xmax = .$Minute[match(task_boundaries_180$Task_End, non_aug$X)]
        ),
        inherit.aes = FALSE,
        aes(
          xmin = xmin,
          xmax = xmax,
          ymin = -Inf,
          ymax = Inf,
          fill = "Task"
        ),
        alpha = 0.4
      ) +
      labs(
        # title = "Vehicle speed time series, highlighting tasks",
        x = "Minute of drive",
        y = "Vehicle speed",
        fill = "Segment"
      ) +
      guides(fill = guide_legend(override.aes = list(alpha = 1))) +
      scale_x_break(c(6, 9))
  } %>%
  {
    ggsave("./output/speed_time_series_highlighted.svg", .)
    print(.)
  }

zoom_plot <- non_aug %>%
  filter(DaqName == non_aug[[1, "DaqName"]]) %>%
  arrange(Frame_Num) %>%
  filter(!rev(cumall(rev(Vehicle_Speed < 60)))) %>%
  mutate(Minute = (Frame_Num + 1 - min(Frame_Num)) / 3600) %>%
  {
    dd <- .
    frame0 <- min(dd$Frame_Num)
    x_to_minute <- function(x) {
      (dd$Frame_Num[match(x, dd$X)] + 1 - frame0) / 3600
    }

    all_rects <- purrr::map_dfr(c("180", "300", "600"), function(frames) {
      seg <- get(glue("task_boundaries_{frames}")) %>%
        filter(Control_Start %in% dd$X) %>%
        mutate(Task_Num = row_number()) %>%
        filter(Task_Num == 4)

      bind_rows(
        tibble(
          xmin = x_to_minute(seg$Control_Start),
          xmax = x_to_minute(seg$Control_End),
          Segment = "Control", Window = frames
        ),
        tibble(
          xmin = x_to_minute(seg$Task_Start),
          xmax = x_to_minute(seg$Task_End),
          Segment = "Task", Window = frames
        )
      )
    })

    bounds_600 <- filter(all_rects, Window == "600")
    pad <- 0.25
    dd %>%
      filter(
        Minute >= min(bounds_600$xmin) - pad,
        Minute <= max(bounds_600$xmax) + pad
      ) %>%
      assign("plot_data", ., envir = parent.frame(2)) %>%
      filter(Correct_Left_Button_Press == 1) %>%
      assign("button_press", ., envir = parent.frame(2))

    ggplot(plot_data, aes(x = Minute, y = Vehicle_Speed)) +
      geom_rect(
        data = all_rects,
        inherit.aes = FALSE,
        aes(
          xmin = xmin, xmax = xmax, ymin = -Inf, ymax = Inf,
          fill = Segment, linetype = Window
        ),
        color = "black",
        alpha = 0.1,
        linewidth = 3 / 4
      ) +
      geom_line() +
      geom_vline(
        data = button_press,
        aes(
          xintercept = Minute
        ),
        color = palette.colors(palette = "Okabe-Ito")[4],
        linewidth = 3 / 4,
        linetype = 1
      ) +
      geom_text(
        data = button_press,
        aes(x = Minute, y = 63.5, label = "Task completion"),
        color = palette.colors(palette = "Okabe-Ito")[4],
        angle = 90,
        vjust = 1.5,
        size = 3.5,
        fontface = "italic"
      ) +
      coord_cartesian(ylim = c(60, 65), expand = FALSE) +
      scale_linetype_manual(
        values = c("180" = "solid", "300" = "dashed", "600" = "dotted")
      ) +
      scale_x_continuous(
        breaks = bounds_600$xmin[bounds_600$Segment == "Task"] +
          (seq(-24, 24, 3) / 60),
        labels = seq(-24, 24, 3)
      ) +
      labs(
        title = "Task 4",
        x = "Seconds after task onset",
        y = "Vehicle speed"
      ) +
      guides(fill = guide_legend(override.aes = list(alpha = 1)))
  }

combined_plots <- as.ggplot(wide_plot + theme(legend.position = "none")) /
  (zoom_plot + theme(legend.position = "bottom")) +
  plot_layout(heights = c(1.2, 1))

ggsave("./output/speed_with_zoom.svg", combined_plots,
  width = 8, height = 7
)
rsvg_pdf("./output/speed_with_zoom.svg", "./output/speed_with_zoom.pdf")
print(combined_plots)
rm(wide_plot, zoom_plot, combined_plots)

# Per_Close odds ratio forest plot
per_close_or_plot <- imap_dfr(models[["per_close"]], function(m, frames) {
  broom.mixed::tidy(
    m,
    effects = "fixed",
    component = "cond",
    conf.int = TRUE,
    exponentiate = TRUE
  ) %>%
    mutate(Window = glue("{as.numeric(frames) / 60}s"))
}) %>%
  filter(term != "(Intercept)") %>%
  mutate(
    term = recode(
      term,
      "BAC" = "BrAC",
      "KSS_cent" = "KSS (median-centered)",
      "PhaseTask" = "Phase (Task)",
      "Road_SurfacePaved" = "Road surface (Paved)",
      "as.numeric(Drive)" = "Drive #",
      "KSS_cent:BAC" = "KSS (median-centered) x BrAC",
      "BAC:PhaseTask" = "BrAC x Phase (Task)"
    ),
    term = factor(
      term,
      levels = rev(c(
        "KSS (median-centered)",
        "BrAC",
        "Phase (Task)",
        "Road surface (Paved)",
        "Drive #",
        "KSS (median-centered) x BrAC",
        "BrAC x Phase (Task)"
      ))
    ),
    window = factor("Segment Length", levels = c("3s", "5s", "10s"))
  ) %>%
  ggplot(aes(x = estimate, y = term, color = Window)) +
  geom_vline(xintercept = 1, linetype = "dashed", color = "darkgray") +
  geom_pointrange(
    aes(xmin = conf.low, xmax = conf.high),
    position = position_dodge(width = 0.6),
    size = 0.4
  ) +
  scale_x_log10() +
  labs(
    x = "Odds ratio (95% CI, log scale)",
    y = NULL,
    color = "Window"
  )

ggsave("./output/per_close_or_plot.svg", per_close_or_plot, width = 8, height = 5)
rsvg_pdf(
  "./output/per_close_or_plot.svg",
  "./output/per_close_or_plot.pdf"
)
print(per_close_or_plot)
```
